---
title: "LGCA"
author: "Valerie Hofmann"
date: "18 1 2022"
output:
pdf_document:
keep_tex: yes
latex_engine: xelatex
html_document:
df_print: paged
header-includes:
- \usepackage{fancyhdr}
- \usepackage{dcolumn}
- \pagestyle{fancy}
- \lhead{01 2 2022}
- \chead{Valerie Hofmann}
- \rhead{Latent Growth Curve Analysis}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
comment = FALSE, fig.align='center', fig.width = 4, fig.height = 4,  echo=FALSE, warning = FALSE, results = 'asis', message = FALSE, root.dir = 'C:/Users/hofma/Desktop/FRESHMO/02_data/'
)
```

# Checking for Multivariate Normal Distribution before Starting the Latent Growth Curve Modelling

```{r, intset, fig.width = 8, fig.height = 8}
#########
# Performing the Latent Growth Curve
#########
#####
library(psych)
library(lme4)
library(lavaan)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(lme4)
library(stargazer)
library(knitr)
library(float)
library(corrplot)
library(dplyr)
library(readr)
library(stargazer)
library(ggpubr)
#library(data.table)
library(tidyverse)
library(caret)

#####
extra_long <- readr::read_csv("C:/Users/hofma/Desktop/LGC/02_data/Extra_BL_to_FU2_nona_long_sum.csv", col_names = TRUE, col_types = cols(ID = "c"))
extra_wide <- readr::read_csv("C:/Users/hofma/Desktop/LGC/02_data/Extra_BL_to_FU2_nona.csv", col_names = TRUE, col_types = cols(ID = "c"))

#colnames(extra_wide)
#colnames(extra_long)

#### Check for Mulitvariate Normal Distribution in Items
dat <-  extra_long %>% select(sleep_duration , "30_min_training" , outside , worried_in_general ,sad_happy , enjoy_activities , relaxed_worried , rumminat , exhausted , concentration , irritable , lonely , neg_toughts , self_harm)
x <- as.matrix(dat)
```



```{r, corp1, fig.width = 10, fig.height = 10}
####corrplott between Items over all time points
resdat <- cor(dat)
resdat <- round(resdat, 2)
col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
corrplot(resdat, method="color", col=col(200),
type="upper", order="hclust",
addCoef.col = "#000000", # Add coefficient of correlation
tl.col="#000000", tl.srt=45, #Text label color and rotation
# hide correlation coefficient on the principal diagonal
diag=FALSE
)
```

## Overview of Items and Scale (German Version)

The IMAGEN Team has create their own questionnaire based on Expert Ratings.
**In the last two weeks**:
1. **EW2W1: worried_in_general** - ...wie besorgt waren Sie im Allgemeinen? - Range: 0 = Überhaupt nicht, 4 = sehr
2. **EW2W2: sad_happy** - ...wie glücklich oder traurig waren Sie? -  Range: 0 = sehr trauig, 4 = sehr glücklich
3. **EW2W3 - enjoy_activities** - ...wie sehr konnten Sie Ihre üblichen Aktivitäten genießen?, Range: 0 = Überhaupt nicht, 4 = sehr
4. **EW2W4 -  relaxed_worried** - ...wie entspannt oder ängstlich waren Sie? Range: 0 = sehr entspannt und ruigh, 4 = sehr nervös
5. **EW2W5 - rumminat** - ...wie zappelig oder unruhig waren Sie? -  Range: 0 = überhaupt nicht zappelig, 4 = sehr zappelig
6. **EW2W6 - exhausted** - ...wie erschöpft oder müde waren Sie? - Range: 0 = überhaupt nicht erschöpft, 4 = sehr erschöpft
7. **EW2W7 - concentration** -  ...wie gut konnten Sie sich konzentrieren oder fokussieren? -  Range: 0 = sehr fokussiert, 4 = sehr unfokussiert
8.**EW2W8 - irritable** - ...wie irritierbar oder reizbar sind Sie gewesen? - Range: 0 = Überhaupt nicht, 4 = sehr
9. **EW2W9 - lonely** - ...wie einsam waren Sie? - Range: 0 = Überhaupt nicht, 4 = sehr
10. **EW2W10 - neg_toughts** - ...inwieweit haben Sie negative Gedanken gehabt und über unangenehme Erfahrungen oder Dinge nachgedacht, die Ihnen ein schlechtes Gefühl bereitet haben? - Range: 0 = Überhaupt nicht, 4 die meiste Zeit
11. **EW2W11 - self_harm** - ...haben Sie absichtlich versucht sich selbst zu verletzen oder weh zu tun? - Range: 0 = überhaupt nicht, 4 = Die meiste Zeit

```{r, checkup, fig.width = 6, fig.height = 6}
##
hist = ggplot(extra_long, aes(x=Symptoms_SUM)) + geom_histogram(color="#000000", fill="#0072B2", alpha=0.6, bins = 30)
hist + scale_x_continuous(limits= c(0, 40)) + scale_y_continuous(limits=c(0, 180)) + theme_bw() + labs(x = "Summed Values of Items", y = "Count", title =  "Symptom Sums Distribution")
#Check if Sums are normal though

s <- shapiro.test(extra_long$Symptoms_SUM)
# da p < 0.05 auch hier keine Normalverteilung anzunehmen, allerdings auch leichte Abweichungen werden signifikant
# widely recommended for normality test and it provides better power than K-S. It is based on the correlation between the data and the corresponding normal scores.
#Note that, normality test is sensitive to sample size. Small samples most often pass normality tests. Therefore, it’s important to combine visual inspection and significance test in # order to take the right decision.
s

```


```{r, checkup_hist, fig.width = 6, fig.height = 6}
multi.hist(dat, bcol = "#0072B2")

##Desnity for Bell Shape
ggdensity(extra_long$Symptoms_SUM, main = "Density plot of Symptom Sums", xlab = "Summed Values", ylab = "Density")

###Corr between Sample and Normal Distribution
ggqqplot(extra_long$Symptoms_SUM, main = "QQ-Plot of Symtom Sums and Normal Distribution",  color = "#999933")

#or quantile-quantile plot) draws the correlation between a given sample and the normal distribution. A 45-degree reference line is also plotted.
ep <- readr::read_csv("C:/Users/hofma/Desktop/LGC/02_data/PHQ9EXTRA_BL_to_FU2_sums.csv", col_names = TRUE, col_types = cols(ID = "c"))

ep_cor <- ep[, c(2,10:20)]
resep <- cor(ep_cor)
resep <- round(resep, 2)
col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
corrplot(resep, method="color", col=col(200),
type="upper", order="hclust",

addCoef.col = "#000000", # Add coefficient of correlation
tl.col="#000000", tl.srt=45, #Text label color and rotation
# hide correlation coefficient on the principal diagonal
diag=FALSE
)
```